%-------------------------
% Resume in Latex
% Author : Syed Emad Uddin Shubha
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}

\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}



\begin{center}
    \textbf{\Huge \scshape Shahidul Haque Shaheen} \\ \vspace{1pt}
    \small Dhaka, Bangladesh $|$ (+880) 1705-157794  $|$ \href{mailto:shahidul.haque.shaheen@gmail.com}{\underline{shahidul.haque.shaheen@gmail.com}} $|$
    \href{https://github.com/ShahidulHaqueShaheeen}{\underline{github.com/ShahidulHaqueShaheeen}} \\ \vspace{1pt}
    \href{https://www.linkedin.com/in/shahidul-haque-shaheen/}{\underline{linkedin.com/in/shahidul-haque-shaheen}}
\end{center}



%-----------Summary-----------
\section{\textbf{PROFILE}}
\justifying{ I am passionate about Data Science, with two years of learning and practical experience. I have strong programming skills and enjoy solving data problems. My dedication to learning helps me constantly improve my abilities and understanding in this field. I am hardworking, determined, and always eager to grow, seeking opportunities to expand my knowledge and make meaningful contributions in Data Science.}

%-----------EDUCATION-----------
\section{\textbf{EDUCATION }}
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{BRAC University} & FALL 2019 – FALL 2023 \\
  B.Sc. in Computer Science and Engineering  & CGPA: 3.58/4.00 \\
\end{tabular*}
\justifying{\textbf{Relevant Courses}: Data Structures, Algorithms, Database Systems, Artificial Intelligence, Neural Networks, Mathematics for Machine Learning and Signal Processing, Machine Learning, Software Engineering. }

%-----------SKILLS----------------------------------------
\section*{\textbf{SKILLS SUMMARY}}
\begin{tabular}{@{}p{0.25\textwidth} p{0.7\textwidth}}
    \textbf{Programming Language} & : Python, SQL, JAVA, HTML, CSS, C, C++.\\
    \textbf{Python Libraries} & : Numpy, Pandas, Matplotlib, Seaborn, Scikit-learn, TensorFlow, Keras.\\
    \textbf{Machine Learning} & : Supervised Learning (Linear Regression, Logistic Regression, Naïve Bayes, Decision Trees Polynomial Regression, Regularization, Gradient Descent),\\ 
    & Unsupervised Learning (K-Means Clustering, Principal Component Analysis (PCA)).\\
    \textbf{Deep Learning} & : Artificial Neural Networks (ANN), Convolutional Neural Networks (CNN), Recurrent Neural Networks (RNN), Long Short-Term Memory (LSTM).\\
    \textbf{Natural Language Processing} & : Text Preprocessing, Tokenization, Sentiment Analysis.\\
    \textbf{Feature Engineering} & : Feature Scaling (Normalization, Standardization), Encoding (One-Hot, Label, Target), Feature Selection (Mutual Information), Dimensionality Reduction (PCA, t-SNE), Handling Missing Data, Outlier Detection.\\
    \textbf{Software} & : Microsoft Power BI, XAMPP, MySQL Workbench. \\
    \textbf{Office Application} & : Excel/Sheets, Word/Docs, PowerPoint/Slides, LaTeX.\\
    \textbf{Soft Skills} & : Organizing, Collaborating, Teaching, Writing. \\
\end{tabular}
    
%-------------------------------------------------------------------------%

\section*{\textbf{NOTABLE PROJECTS}}
\begin{itemize}[left=0cm]
    \setlength\itemsep{-0.075em} % Adjust the spacing between items
    \setlength\parskip{-0.075em} % Adjust the spacing between paragraphs within items

    \item Real Estate Price Prediction using Data Science - \href{https://github.com/ShahidulHaqueShaheeen/Real_Estate_Price_Prediction.git}{\underline{\textbf{GitHub Link}}}.
    \begin{itemize}[left=0cm]
        \item[-] \small \justifying Developed a predictive model to estimate real estate prices based on historical data.
        \item[-] \small \justifying Used Python with Pandas, NumPy, and Scikit-Learn for data preprocessing and model building.
        \item[-] \small \justifying Implemented regression algorithms like Linear Regression and DecisionTreeRegressor.
        \item[-] \small \justifying Evaluated model performance using Cross Validation and GridSearchCV.
    \end{itemize}
    
    \item Spam Message or Email Detector using Machine Learning - \href{https://github.com/ShahidulHaqueShaheeen/Spam_MessageOrMail_Detector.git}{\underline{\textbf{GitHub Link}}}.
    \begin{itemize}[left=0cm]
        \item[-] \small \justifying Built a classifier to detect spam messages and emails with high precision.
        \item[-] \small \justifying Applied NLP techniques like tokenization and TF-IDF vectorization.
        \item[-] \small \justifying Used Python with Scikit-Learn to train models, including Naïve Bayes.
        \item[-] \small \justifying Evaluated model performance using accuracy, precision, and recall.
    \end{itemize}

    \item SQL Case Study on Data Science Job Salaries - \href{https://github.com/YOUR_GITHUB_LINK}{\underline{\textbf{GitHub Link}}}.
    \begin{itemize}[left=0cm]
        \item[-] \small \justifying Conducted SQL-based case studies on real-life datasets to analyze job salaries in data science.
        \item[-] \small \justifying Used SQL queries to extract insights and answer business-related questions.
        \item[-] \small \justifying Organized the case study into structured components: Question, Query, and Output.
    \end{itemize}

    \item Machine Learning Algorithm Implementations - \href{https://github.com/YOUR_GITHUB_LINK}{\underline{\textbf{GitHub Link}}}.
    \begin{itemize}[left=0cm]
        \item[-] \small \justifying Implemented fundamental ML algorithms like Gradient Descent, Linear Regression, and Logistic Regression.
        \item[-] \small \justifying Explored Polynomial Regression and Regularization techniques (Lasso, Ridge) to prevent overfitting.
        \item[-] \small \justifying Used NumPy, Pandas, and Scikit-Learn for model building and experimentation.
        \item[-] \small \justifying Provided clear explanations and code implementations for understanding core ML principles.
    \end{itemize}

    \item Exploring Data With Pandas - \href{https://github.com/ShahidulHaqueShaheeen/Exploring-Data-with-Pandas.git}{\underline{\textbf{GitHub Link}}}.
    \begin{itemize}[left=0cm]
        \item[-] \small \justifying Explored Pandas Series and DataFrame operations with real-world datasets.
        \item[-] \small \justifying Performed data manipulation, cleaning, and preprocessing tasks.
        \item[-] \small \justifying Conducted exploratory data analysis (EDA) and generated analytical insights.
        \item[-] \small \justifying Applied Pandas functions like GroupBy, Pivot Tables, and Merging datasets.
        \item[-] \small \justifying Used NumPy, Matplotlib, and Seaborn for data visualization and deeper analysis.
    \end{itemize}

\end{itemize}


%-----------Research-----------

\section*{\textbf{RESEARCH EXPERIENCE}}
\subsection*{Undergraduate Research / Thesis | BRAC University - 
 \href{https://github.com/ShahidulHaqueShaheeen/Research_Thesis.git}{\underline{\textbf{GitHub Link}}}.}


\begin{itemize}[left=0cm]
    \setlength\itemsep{-0.025em} % Adjust the spacing between items
    \setlength\parskip{-0.025em} % Adjust the spacing between paragraphs within items
    \fontsize{9.6}{11.2}\selectfont
  \item Conducted an undergraduate thesis on Deep Learning (Image Classsification) under the supervision of Dr. Jannatun Noor.
  \item \textbf{Title :} CattleSavior: Towards Implementing an Advanced External Disease Detection System through Deep Learning.
\end{itemize}


\section*{\textbf{RESEARCH INTEREST}}
\begin{minipage}[t]{0.33\textwidth}
  \begin{itemize}[left=0cm]
    \setlength\itemsep{-0.075em} % Adjust the spacing between items
    \setlength\parskip{-0.075em} % Adjust the spacing between paragraphs within items
    \item Machine Learning
    \item Deep Learning
  \end{itemize}
\end{minipage}%
\begin{minipage}[t]{0.33\textwidth}
  \begin{itemize}[left=0cm]
    \setlength\itemsep{-0.075em} % Adjust the spacing between items
    \setlength\parskip{-0.075em} % Adjust the spacing between paragraphs within items
    \item Image Processing
    \item Natural Language Processing
  \end{itemize}
\end{minipage}%
\begin{minipage}[t]{0.33\textwidth}
  \begin{itemize}[left=0cm]
    \setlength\itemsep{-0.075em} % Adjust the spacing between items
    \setlength\parskip{-0.075em}
    \item Human Computer Interface
    \item Generative artificial intelligence
  \end{itemize}
\end{minipage}




\section*{\textbf{REFERENCES}}
\begin{tabular}{@{}p{0.45\textwidth} p{0.5\textwidth}}
    Jannatun Noor Mukta, & Moin Mostakim, \\
    Assistant Professor, CSE Department, & Senior Lecturer, CSE Department, \\
    BRAC University, Dhaka. & BRAC University, Dhaka. \\
    Email: jannatun.noor@bracu.ac.bd & Email: mostakim@bracu.ac.bd \\
\end{tabular}


\end{document}
